\documentclass[11pt]{article}

\usepackage{exscale}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{times,mathptm}
\usepackage{epsfig}
\usepackage{setspace}

\textwidth 6.5truein          
\textheight 9.0truein
\oddsidemargin 0.0in
\topmargin -0.6in

\parindent 0pt          
\parskip 5pt
\def\baselinestretch{1.1}

\begin{document}

\begin{LARGE}
\centerline {\bf CSci 423 Homework 9}
\end{LARGE}
\vskip 0.25cm

\centerline{Due: 1:00 pm, Wednesday, 11/14}
\centerline{Eric Shih}

\begin{enumerate}
  \item (7 points) Exercise 4.3 on page 183. \\
    A decidable language is closed under the complement. TM $M_{\bar{L}}$ which decides $\bar{L}$ will accept when TM $M_{\bar{L}}$ that
    decides $L$ rejects, and reject when $M_{\bar{L}}$ accepts. It has been shown that $E_{DFA}$ is decidable where $E_{DFA}$ = $\{<A> | $
    is a DFA and $L(A)= \emptyset \}$. \\
    On input $<A>$ where $A$ is a DFA:
    \begin{enumerate}
     \item Mark the start state of $A$.
     \item Repeat until no new states are marked.
     \item Mark states that has a transition coming in from any state that is already marked.
     \item If no accept state is marked, accept. Otherwise, reject.
    \end{enumerate}

  \item (7 points) Exercise 4.6 on page 183. \\
    Proof by contradiction. Assume that $B$ is countable. Infinate sequences over ${0,1}$ can be represented by $N = {1,2,3,...}$. A
    $f(n)$ can be mapped where $n \in N$. $f(n) = (w_{n1},w_{n2},w_{n3},...)$ where $w_{ni}$ is the $i$th bit in the $n$th sequence. Using
    diagonalization, it is possible to find a sequence over ${0,1}$ that is not in $f(n)$, where the $i$th bit is the opposite of the $i$th
    sequence. This means that the sequences are $\notin$ $B$, giving us a contradiction, proving $B$ to be uncountable. \\
    $
    \begin{array}{l|l}
     $n$ & f(n) \\ \hline
     $1$ & (w_1 1, w_1 2,w_1 3,w_1 4,...) \\
     $2$ & (w_2 1, w_2 2,w_2 3,w_2 4,...) \\
     $3$ & (w_3 1, w_3 2,w_3 3,w_3 4,...) \\
     \vdots & \vdots
    \end{array}
    $
  \item (7 points) Exercise 4.7 on page 183. \\
  *reference www.cs.ucdavis.edu/~gusfield/cs120f11/HW6key.pdf* \\
  To prove that T is countable we provide a function f : T → N. Given a triple (i, j, k)
from T f is deﬁned as follows: convert each number i, j, and k to their respective binary
representation. We will compute the natural number n in its binary representation. For
the ath bit of n, we divide a by 3. This will produce a quotient q and a remainder r.
If r is 0 then we extract the qth bit from i, if r is 1 then we extra the qth bit from j,
if r is 2 then we extract the qth bit from k. Note that if the qth bit of i, j, or k is not
deﬁned then use a 0. Note that f maps every i, j, k tuple to a natural number and every
natural number can be converted to an i, j, k tuple (by the reverse process). Hence f is
a one-to-one function and onto (aka a bijection). Therefore T is countable.

  \item (7 points) Problem 4.19 on page 184. \\
  *test.scripts.psu.edu/users/a/y/.../Decidable\%20Languages(2).docx* \\  
	Let P = ADFA. We know this to be decidable. \\
	We also know that regular languages are closed under the reverse operation. So, if there is a DFA D for
	w, there is a DFA D’ for $w^R$. We can then construct an NFA N by branching to D and D’. Since we have
	an algorithm to convert NFAs to DFAs, we run it on $<N>$ to get $<M>$. Now we have a DFA M, and since
	ADFA is decidable, there is some S such that S = $\{<M>\}$. Since M is a DFA that accepts wR whenever it
	accepts w, $S = \{<M> | M$ is a DFA that accepts $w^R$ whenever it accepts $w\}$, and S is decidable.
  
  \item (12 points) In class, we learned that $A_D$ is non-TR, $A_{TM}$ and $HALT_{TM}$ are TR but non-TD. What can you say 
	about their complements? Are they non-TR, TR but non-TD, or TD? Justify your answers. \\
	
	Both $\bar{A_{TM}}$ and $\bar{HALT_{TM}}$ are not TR since $A_{TM}$ and $HALT_{TM}$ are TR. If both sets were TR, then
	they would also be TD. \\
	$\bar{A_D}$ is not TD, according to the closure property, because $A_D$ is not TD. $\bar{A_D}$ is, on the other hand, TR.
	In the case $A_D = \{w_i | w_i \notin L(M_i) \}$, its complement $\bar{A_D} = \{w_i | w_i \in L(M_i) \}$. A TM R can be
	constructed to take $w_i$ as input, then use the string to code TM $M_i$. Both are then fed into $A_TM$, which will accept
	if it accepts. This shows that $\bar{A_D}$ is TR.
\end{enumerate}

\pagebreak
\setlength{\parindent}{1cm}
\centerline{\bf Reading Summary 4}

\begin{spacing}{1.5}
 \indent The turing machine is far from being bettered by other models. Over 75 years, the Turing Machine is still considered the best machine
 model availble. It can be used to model both modern computing and the natural world. What we have learned over the years in computing is a
 result of the model. \\
 \indent The Turing machine was so special because it disembodied the machine and broadened the view of computation. It brought the view away
 from what goes specifically into the machine, but how the machine reacts and works as a whole. There are also challenges to the standard model,
 which all have an impact on universality. The most generally respected challenge to the model is that ``one can apply it ever more widely to what
 we observe in nature, and let it mold our expectations of what computing machines can achieve.
\end{spacing}


\end{document}
